Notes

### 2019-11-01 Notes.Rmd
week1 notes

>>>>

## Regular exp notes

whitespace word boundaries

sets of literals

beginnig and end of a line

alternatives (word1 or word2)

- Start of a line
"^i think"

- end of the line
"morning$"

- sets of characters
"[Bb][Uu][Ss][Hh]"
all case alternatives for the word in e.g. BUSH, BuSH, Bush, bush, bUSH

- all letters from a to z (uppercase or lower case)or numbers from 0 to 9, in the beginning of a line
"^[0-9][a-zA-Z]"

- when you use ^ at the beginning of a character class, it is a metacharacter indicating logical NOT operator.
"[^?.]$"  means = any lines NOT ending with a question mark or a period.

- "any" metacharacter
"9.11" means= 9 followed by any character followed by 11

- "or" metacharacter
"flood|fire|coldfire" will match flood or fire or coldfire

- you can combine
"^[Gg]ood|[Bb]ad" will match Good/good in the beginning of a line or Bad/bad anywhere

"^([Gg]ood|[Bb]ad)" will match Good/good or Bad/bad in the beginning of a line

- "optional" metacharacter
"[Gg]eorge( [Ww]\.)? [Bb]ush" will match where whitespace + [Ww] + . is optional

- backslash escapes metacharacter so . means any character, \. means period

- repetitions
"*" means repeat any number of times, including none
"+" means at least one

"(.*)" will match any character of any number
